Untitled

### 2024-02-19 MSR.rmd
Update

```{r}
k<-1000 # ulangan
n<-5 #banyak sampel
set.seed(15)
y21<-matrix(-rexp(n*k),k) #bangkitkan sampel
hist(y21)

@@

yy22<-apply(y22,1,mean) #simpan rataan
hist(yy22, main = "Sebaran Percontohan Eksponensial Negatif 50 Sampel")

yy23<-apply(y23,1,mean) #simpan rataan
hist(yy23, main = "Sebaran Percontohan Eksponensial Negatif 500 Sampel")
```

>>>>

```{r}
k<-1000 # ulangan
n<-5 #banyak sampel
par(mfrow=c(3,3))

set.seed(15)
y21<-matrix(-rexp(n*k),k) #bangkitkan sampel
hist(y21)

yy23<-apply(y23,1,mean) #simpan rataan
hist(yy23, main = "Sebaran Percontohan Eksponensial Negatif 500 Sampel")

@@

yy22<-apply(y22,1,mean) #simpan rataan
hist(yy22, main = "Sebaran Percontohan Eksponensial Negatif 50 Sampel")
```
